### 2021-05-05 doc/thesis/chapters/dsp.tex
more splitting into files

  \section{Frequency Modulation (FM)}
  see literature/Present\_lec6\_AM\_FM.pdf\\
  see lectures out of HSD/ESD
    \subsection{Mathematical description}
    \subsection{Frequency Band, Channel allocation/distribution}

@@

%%%%%%%%%%%%%%%%%%%%
\chapter{Implementation}
  \section{Matlab/Python Model}
  in fixed point, close to hardware level algorithm

  \section{VHDL (no shortcut)}
    \subsection{Channel Selection (IF to Channel-BB)}
    \subsection{Phase Detector}
    \subsection{other Elements}

  \section{High-Level Synthesis}
    \subsection{Channel Selection (IF to Channel-BB)}
    \subsection{Phase Detector}
    \subsection{other Elements}

  \section{Common Testbench}
    \subsection{Architecture (same tb for VHDL and HLS-generated HDL)}
    \subsection{Framework cocotb, with ghdl compiler}
        Instantiate both HDL models in the testbench.\\
        Display a direct comparison of outputs in graphs. This is practical, since the cocotb framework runs in python and graphs can be generated using Python's matplotlib.

  \section{Develop HLS compiler independent code (optional)}
    \subsection{Challenges}
     Different compilers use different \#pragmas, etc.\\
     The \#pragmas need to be within the code, at the appropriate positions, which makes it difficult to write compiler independent code....

\chapter{Test Results}
  \section{Functionality}
  % Functionality same?
  % Sim speed of x min of recorded FM signal
  % lines of code
  \subsection{Implementation effort/time}
  \subsection{Hardware Utilization}
  \subsection{Others}

  % TODO Überlegungen in diesem Kapitel
  % kann Demodulator geändert werden? Bsp. von FM zu DAB+, QAM, etc..
  % - von matlab heraus VHDL generieren, etc

%%%%%%%%%%%%%%%%%%%%
\chapter{Deployment on Hardware}
  \section{Hardware Platform}
    \subsection{RTL2832u Dongle}
    \subsection{ZedBoard}

>>>>

  \section{Frequency Modulation (FM)}
  see literature/Present\_lec6\_AM\_FM.pdf\\
  see lectures out of HSD/ESD

  Frequency modulation (FM) is a widely used standard to transmit data streams.
  The probably best known usecase therefore is commercial broadcast radio, where an audio stream is transmitted.
  Devices to receive these streams are available starting from affordable low prices to the public.

    \subsection{Mathematical description}
    \subsection{Frequency Band, Channel allocation/distribution}

@@

### 2021-05-05 doc/thesis/chapters/implementation.tex
more splitting into files

%%%%%%%%%%%%%%%%%%%%
\chapter{Signal Processing Theory}
\label{cha:TheThesis}

  \section{Modulation from Baseband to RF}
  \section{Modulation from RF to Baseband}

  \section{Frequency Modulation (FM)}
  see literature/Present\_lec6\_AM\_FM.pdf\\
  see lectures out of HSD/ESD
    \subsection{Mathematical description}
    \subsection{Frequency Band, Channel allocation/distribution}

  \section{Algorithms for Digital FM Demodulation}
    see literature/FmDemodulator.pdf (Sect. 3.3)
    see literature/00476180 Digital FM Demodulator for FM, TV, and Wireless.pdf (Sect. II and III)

    \subsection{Baseband Delay Demodulator}
    \subsection{Phase-Adapter Demodulator}
    \subsection{Phase-Locked Loop (PLL)}
    \subsection{Mixed Demodulator}

%%%%%%%%%%%%%%%%%%%%
\chapter{High-Level Synthesis}
  \section{Introduction / State of the Art}
  \section{Functionality (transform high-level code to HDL)}
  \section{Language Support}
    \subsection{C++}
    \subsection{SystemC}
  \section{Coding}
    \subsection{Compiler Directives (\#pragma's)}
    \subsection{Data types}
    \subsection{Functions}
    \subsection{Loops}
    \subsection{Conditional statements}
  \section{Advantages / Disadvantages}
    easy and much faster to get complex HDL code, such as image/video processing, through libraries like OpenCV. However, it is less optimized, and a developer still needs to have a strong hardware background, to be able to understand what is being generated in hardware from x lines of code in HLS/Cpp.

%%%%%%%%%%%%%%%%%%%%
\chapter{System Architecture/Concept}
  \section{Block Diagram (with details)}
    \subsection{describe blocks}
  \section{Which parts in HLS and VHDL}
  \section{Test Environment}

%%%%%%%%%%%%%%%%%%%%
\chapter{Implementation}
  \section{Matlab/Python Model}
  in fixed point, close to hardware level algorithm

@@

\chapter{Test Results}
  \section{Functionality}
  % Functionality same?
  % Sim speed of x min of recorded FM signal
  % lines of code
  \subsection{Implementation effort/time}
  \subsection{Hardware Utilization}
  \subsection{Others}

  % TODO Überlegungen in diesem Kapitel
  % kann Demodulator geändert werden? Bsp. von FM zu DAB+, QAM, etc..
  % - von matlab heraus VHDL generieren, etc

%%%%%%%%%%%%%%%%%%%%
\chapter{Deployment on Hardware}
  \section{Hardware Platform}
    \subsection{RTL2832u Dongle}
    \subsection{ZedBoard}

>>>>

%%%%%%%%%%%%%%%%%%%%
\chapter{Implementation}
\label{cha:Implementation}
\section{Matlab/Python Model}
  in fixed point, close to hardware level algorithm

@@
